---
title: "GitHub branches using RStudio"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Is your fav' iconic !?!

Write and R script to compare the csv with your favorite desserts you modified previously with the top 42 most iconic American desserts 

1. Create a new branch using RStudio
2. Add a new script named `desserts_match_myinitials.R` 
3. This script should read both csv files into R and try to determine if your favorite dessert is part of the most iconic desserts!

You can download the iconic data here: <https://github.com/brunj7/EDS-214-analytical-workflows/blob/main/data/iconic_desserts.csv>

## Note

Here is how we created the iconic listing

```{r getting the data, eval=FALSE}
library(tidyverse)
library(rvest)

# read the webpage code
webpage <- read_html("https://www.eatthis.com/iconic-desserts-united-states/")

# Extract the desserts listing
dessert_elements<- html_elements(webpage, "h2")
dessert_listing <- dessert_elements %>% 
  html_text2() %>% # extracting the text associated with this type of elements of the webpage
  as_tibble() %>% # make it a data frame
  rename(dessert = value) %>% # better name for the column
  head(.,-3) %>% # 3 last ones were not desserts 
  rowid_to_column("rank") %>% # adding a column using the row number as proxy for the rank
  write_csv("data/iconic_desserts.csv") # save it as csv

```

