---
title: "Documenting things"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(reticulate)
```


## The power of README

README are not a new thing. They have been around computer projects since the early days. One great thing about the popularization of supporting the markdown syntax and its web rendering in most code repositories, is that you can move beyond a simple text file and start to present a compelling entry point to your project that can link to various parts and external resources.



## Making your code readable

It is important to make your code easy to read if you hope that others will reuse it. It starts with using a **consistent syntax** withing your scripts (at least within a project). 

- Here is a good style guide for R: http://adv-r.had.co.nz/Style.html
- Syle guide for Python: https://www.python.org/dev/peps/pep-0008/

```{python Zen of Python, echo=TRUE}
import this
```


There is also the **visual aspect** of the code that should not be neglected. Like a prose, if you receive a long text without any paragraphs, you might be not very excited about reading it. _Indentation_, _spaces_, and _empty lines_ should be leveraged to make a script visually inviting and easy to read. The good news is that most of the Integrated Development Environment (IDE) will help you to do so by auto formatting your scripts according to conventions.  Note that also a lot of IDEs, such as RStudio, rely on some conventions to ease the navigation of scripts and notebooks. For example, try to add four `-` or `#` after a line starting with one or several `#` in an R Script! 

## Comments

***Real Programmers don't comment their code. If it was hard to write, it should be hard to understand.*** \
_Tom Van Vleck, based on people he knew (https://multicians.org/thvv/realprogs.html)_

Joke aside, it is really hard to comment too much your code, because even steps that might seem trivial today might not be so anymore in a few weeks or months for now. In addition, a well commented code is more likely to be read by others. Note also that comments should work in complement of the code and should not being seen as work around vague naming conventions of variables or functions.

```{r , eval=FALSE}
x <- 9.81  #  gravitational acceleration

gravity_acc <- 9.81  # earth gravitational acceleration
```


### Header

It is good to add a header to your script that will provide basic information such as:

- Purpose of the script (Long title style)
- Who are the authors
- A contact email 

Optional:

- A longer description about the script purpose
- A starting date and potentially last updated one, although this information becomes redundant with repository information

Note that R Studio does something similar by default when creating an new R Markdown document!

### Inline 

It does not matter if you are using a script or notebook. It is important to provide comments along your code to complement it by:

- explaining what the code does
- capturing decisions that were made on the analytical side. For example, why a specific value was used for a threshold.
- specifying when some code was added to handel an edge case such as an unexpected value in the data (so a newuser doesn't have to guess what does lines of code and might want to delete them assuming it is not necessary)

Other thoughts:

- It is OK to state (what seems) the obvious
- Try to keep it to the point



### Functions






## Leveraging Notebooks

### A few thoughts on Notebooks and Scripts

## Hands-on

Let's try to improve the readability and documentation of this repository: <https://github.com/brunj7/better-comments>

Follow the instructions on the README


## Metadata

### Human readable

### Machine readable

### Data provenance & semantics



## Licensing

It is a good practice to add a license to a repository / project. It will help to clarify what are the expectations regarding using and potentially contributing to this work. 

Here is a good website to choose a license: 

Here is also good set of instructions on how to make this happen on a GitHub repository: https://docs.github.com/en/github/creating-cloning-and-archiving-repositories/creating-a-repository-on-github/licensing-a-repository

Note that for content (such as this course), there is also another type of licensing that can be used: https://creativecommons.org/licenses/

## Further Reading

- Python Hichhiker's guide: https://docs.python-guide.org/writing/style/
- Roxygen2: https://cran.r-project.org/web/packages/roxygen2/vignettes/roxygen2.html
- Introduction to Software Engineering by Jason Coposky: https://github.com/NCEAS/training/blob/master/2014-oss/day-09/IntroductionToSoftwareClass.pdf
- Functional programming in R: http://adv-r.had.co.nz/Functional-programming.html#functional-programming
- Scoping in R: http://adv-r.had.co.nz/Functions.html
- https://www.quora.com/What-is-the-difference-between-programming-languages-markup-languages-and-scripting-languages
- http://stackoverflow.com/questions/17253545/scripting-language-vs-programming-language




